Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-01-11 src/ms.tex
paper edits

\newcommand{\taucz}{$\tau_\mathrm{cz}$\xspace}
\newcommand{\rocrit}{$\mathrm{Ro_{crit}}$\xspace}
\newcommand{\rocritfinal}{$\mathrm{Ro_{crit}}~\lesssim~2$\xspace}
\newcommand{\lamostkep}{LAMOST--Kepler\xspace}
\newcommand{\lamostmcq}{LAMOST--McQuillan\xspace}
\newcommand{\teffmin}{5500~K\xspace}
\newcommand{\agerange}{$\sim$2--6~Gyr\xspace}
\newcommand{\agemin}{$\sim$2--3~Gyr\xspace}

@@

\textbf{We matched 10844 LAMOST targets to 10650 unique Kepler IDs in the \citet{McQuillan2014} sample. In the \citet{Santos2021} sample we found 54982 unique cross-matched sources in LAMOST, of which 18990 have published temperatures and rotation periods. For the Kepler sources with duplicate cross-matched LAMOST sources we kept the source with a brighter Gaia DR2 $G$ magnitude. We additionally selected sources with 3000~K~$<~\teff~<$~8000~K, 3~$<$~\logg~$<$~5~dex, and -2~$<$~[Fe/H]~$<$~2~dex. The final sample contains 10516 unique targets with well-determined \prot and \teff (having a median error of 24~K). The metallicity distribution of the LAMOST--McQuillan sample is centered near solar, with a mean and standard deviation of -0.1~dex and 0.26~dex, respectively. There is negligible overlap (3 stars) between our LAMOST--McQuillan sample and the CKS sample since the \citet{McQuillan2014} did not publish rotation periods for KOIs, which were the targets of the CKS project. Rotation periods for KOIs are instead published in \citet{McQuillan2013}, as discussed in \S\ref{subsec:cks}.}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{./figures/lamost-mcquillan.pdf}
    \includegraphics[width=\textwidth]{./figures/lamost-santos.pdf}
    \caption{}
    \label{fig:xmatch}
\end{figure*}

@@

\begin{acknowledgments}
We thank Rodrigo Luger for helpful discussions and assistance with the \texttt{showyourwork!} package, and Adrian Price-Whelan for providing the APOGEE--Kepler cross-match catalog. It is a pleasure to thank the Stars Group at the American Museum of Natural History, and the Astronomical Data Group at the Flatiron Institute for helpful discussions.

>>>>

\newcommand{\taucz}{$\tau_\mathrm{cz}$\xspace}
\newcommand{\rocrit}{$\mathrm{Ro_{crit}}$\xspace}
\newcommand{\rocritfinal}{$\mathrm{Ro_{crit}}~\lesssim~2$\xspace}
\newcommand{\lamostkep}{LAMOST--Kepler\xspace}
\newcommand{\lamostmcq}{LAMOST--McQuillan\xspace}
\newcommand{\lamostsan}{LAMOST--Santos\xspace}
\newcommand{\teffmin}{5500~K\xspace}
\newcommand{\agerange}{$\sim$2--6~Gyr\xspace}
\newcommand{\agemin}{$\sim$2--3~Gyr\xspace}

@@

\textbf{We matched 10844 LAMOST targets to 10650 unique Kepler IDs in the \citet{McQuillan2014} sample. In the \citet{Santos2021} sample we found 54982 unique cross-matched sources in LAMOST, of which 18990 have published temperatures and rotation periods. For the Kepler sources with duplicate cross-matched LAMOST sources we kept the source with a brighter Gaia DR2 $G$ magnitude. We additionally selected sources with 3000~K~$<~\teff~<$~8000~K, 3~$<$~\logg~$<$~5~dex, and -2~$<$~[Fe/H]~$<$~2~dex. The final sample contains 10516 unique targets with well-determined \prot and \teff (having a median error of 24~K). The metallicity distribution of the LAMOST--McQuillan sample is centered near solar, with a mean and standard deviation of -0.1~dex and 0.26~dex, respectively. There is negligible overlap (3 stars) between our LAMOST--McQuillan sample and the CKS sample since the \citet{McQuillan2014} did not publish rotation periods for KOIs, which were the targets of the CKS project. Rotation periods for KOIs are instead published in \citet{McQuillan2013}, as discussed in \S\ref{subsec:cks}. Visualizations of the \lamostmcq and \lamostsan samples are shown in Figure~\ref{fig:xmatch}.}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{./figures/lamost-mcquillan.pdf}
    \includegraphics[width=\textwidth]{./figures/lamost-santos.pdf}
    \caption{Two-dimensional histograms indicating the number of Kepler target stars in the \teff–\prot plane for the \lamostmcq sample (top row) and the \lamostsan sample (bottom row). The effects of a simple cut in \logg to separate subgiants and dwarfs are shown in the middle and right columns. In each panel the Sun is indicated by the orange point, with an errorbar reflecting the range of periods measured from its differentially rotating surface. The long-period pile-up for dwarf stars is clearly seen to extend to the solar temperature. The short-period pile-up is most clear in the \lamostmcq sample.}
    \label{fig:xmatch}
\end{figure*}

@@

\begin{acknowledgments}
We thank Rodrigo Luger for helpful discussions and assistance with the \texttt{showyourwork!} package, Adrian Price-Whelan for providing the APOGEE--Kepler cross-match catalog, and Karl Jaehnig for plotting advice. It is a pleasure to thank the Stars Group at the American Museum of Natural History, and the Astronomical Data Group at the Flatiron Institute for helpful discussions.
